---
title: "DDP Week 4 Assignment"
author: "Tyler Oberembt"
date: "February 1, 2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

 - This presentation is part of the assignemnt for week 4, ***Developing Data Products course from Coursera***
 
 - The presentation is about the second half of the above mentioned assignment (a development project). 

 - The presentation was generated using ***RStudio***(<https://www.rstudio.com>)

## Application

 - The second half of the assignment was to develop a web application using shiny. The application was named ***Predicting the MPG of a car***. Here is the location of the app <https://toberembt.shinyapps.io/Predicting_the_MPG_of_a_car/>.
 
 - Within the app, a prediction model is generated, based on a dataset that includes information about various types of cars (Horsepower, weight, transmission, etc.). The user can experiment with the UI values in order to simulate the variables of a car and be able to predict its MPG consumption.
 
 - The application and the current presentation source codes can be found at <https://github.com/toberembt/DDP_Week4>. The application comprises 3 files: *ui.R* (UI), *server.R* (backend) and *modelBuilding.R* (Random Forest predictor).
  
## MT Cars Dataset

Dataset used by the application is the [Motor Trend Car Road Tests](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/mtcars.html) (from now on *'mtcars'*). The data was extracted from the ***1974 Motor Trend*** US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

Lets look at the dataset structure: 
```{r cars, echo = TRUE}
str(mtcars)
```

## Prediction Model

I decided to use a Random Forest prediction model and trained the model using the *'mtcars'* dataset. My overall goal is to predict the fuel consumption based on the rest of the variables:
```{r echo = FALSE}
suppressWarnings(suppressMessages(library(caret)))
suppressWarnings(suppressMessages(library(randomForest)))

set.seed(2018)

```

```{r echo = TRUE}
customTrainControl <- trainControl(method = "cv", number = 10)
carsRandomForestModelBuilder <- function() {
  return(
    train(
      mpg ~ ., 
      data = mtcars,
      method = "rf",
      trControl = customTrainControl
    )
  )
}

carsRandomForestModelBuilder()
```
